Bird Density, with Edge ML

### 2019-07-03 report/paper.tex
Added some info about mel spaced filter banks.

>>>>

\subsection{Mel Spaced Filter Bank}
Human hearing sensitivity works in a very nonlinear way. For a human, there is a stark difference between a signal that is 50hz and a signal that is 150hz. However is it almost impossible to notice a difference between a a 10khz signal and a 11khz signal. The mel scale has been developed to represent this. It it shown in Equation \ref{mel-eq} and is plotted in Figure \ref{mel}.

\begin{equation}
M(f) = 1125 \cdot log(1+\frac{f}{700})
\label{mel-eq}
\end{equation}

\begin{figure}[h]
\includegraphics[width=9cm]{mel.eps}
\caption{The Mel Scale}
\label{mel}
\end{figure}

To get more adequate feature extraction we are going to use a mel spaced filter bank. This effectively maximizes the features extracted as a function of the mel scale. The filter array is shown in Figure \ref{FA}. In this example we have implemented ten filters for visulizing purposes, however in practice we are going to implement over twenty.

\begin{figure}[h]
\includegraphics[width=9cm]{FA.eps}
\caption{The Mel Scale}
\label{FA}
\end{figure}
